A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-03-18 paper/discussion.tex
Paper: initial results

\begin{figure}
\epsscale{1.00}
\plotone{fig/cosmic_variance.pdf}
\caption{Cosmic Variance: The Luminosity Function is made using the DMH catalog 
from the full box and the set of parameters from the small boxes.}
\label{graph_cosmic_variance}
\end{figure}

\citep{lundgren14} SFR evolution from $z=1$ to $6$

\citep{bouwens14} HST Legacy

\citep{jiang11} Keck pectroscopy

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/scattering_plots.png}
\caption{Covariance of parameters for one small box}
\label{graph_scattering_plots}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
\label{graph_SFR_DMHM_w}
\end{figure}

>>>>

%\citep{lundgren14} SFR evolution from $z=1$ to $6$

%\citep{bouwens14} HST Legacy

%\citep{jiang11} Keck pectroscopy

@@

### 2015-03-18 paper/the_bibliography.tex
Methodology: Dust attenuation
Paper: initial results

\bibitem[Bouwens et al.(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
% Observational luminosity function

@@

\bibitem[Col\'in et al.(1999)]{colin99}
Col\'n, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
1999, \apj , 523,32
% Halo Abundance Matching
\bibitem[Conroy et al.(2006)]{conroy06}
Conroy, Charlie, Risa H. Wechsler, \and Andrey V. Kravtsov. 2006, \apj,647,201
% Halo Abundance Matching

@@

@@

\bibitem[Law et al.(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[Jiang et al.(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
		%2011ApJ...743...65J
\bibitem[Lee et al.(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
		%2009ApJ...695..368L
\bibitem[Lundgren et al.(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
34		%2014ApJ...780...34L
\bibitem[Madau et al.(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
		%1998ApJ...498..106M
\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster et al.(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903

@@

>>>>

\bibitem[Bouwens et al.(2012a)]{bouwens12} Bouwens, R. J. et al. 2012a, \apj, 752, 5 	
		%2012ApJ...752L...5B
% Observational luminosity function

\bibitem[Bouwens et al.(2012b)]{bouwens12b} Bouwens, R. J., G. D. Illingworth, 
P. A. Oesch, M. Franx, I. Labbé, M. Trenti, P. van Dokkum, et al. 2012b. \apj, 754,83
% Dust Attenuation

@@

\bibitem[Col\'in et al.(1999)]{colin99}
Col\'in, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
1999, \apj , 523,32
% Halo Abundance Matching
\bibitem[Conroy et al.(2006)]{conroy06}
Conroy, Charlie, Risa H. Wechsler, \and Andrey V. Kravtsov. 2006, \apj,647,201
% Halo Abundance Matching

@@

\bibitem[Gonzalez-Perez et al(2014)]{gonzalez14}
Gonzalez-Perez, V., C. G. Lacey, C. M. Baugh, C. D. P. Lagos, J. Helly, D. J. R. Campbell, and P. D. Mitchell. 2014.\mnras, 439, 264
% GALFORM semi-analytical model

@@

\bibitem[Law et al.(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[Jiang et al.(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
		%2011ApJ...743...65J
\bibitem[Lee et al.(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
		%2009ApJ...695..368L
\bibitem[Lundgren et al.(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
34		%2014ApJ...780...34L
\bibitem[Madau et al.(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
		%1998ApJ...498..106M
\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, 
\and O. Almaini. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M

\bibitem[Meurer et al.(1999)]{meurer99} Meurer, Gerhardt R., Timothy M. Heckman, 
\and Daniela Calzetti. 1999, \apj, 521, 64
% Dust Attenuation

\bibitem[Moster et al.(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903

@@

\bibitem[Smit et al.(2012)]{smit12} Smit, Renske, Rychard J. Bouwens, Marijn Franx, Garth D. 
Illingworth, Ivo Labbé, Pascal A. Oesch, \and Pieter G. van Dokkum. 2012, \apj 756,14
% Dust Attenuation
